Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-11-24 RR_manuscript/Draft_RR.tex
cleanup merge mess

Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.

@@

Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code {[}if applicable{]}, and a detailed journal-ready statistical methods section.

@@

After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: \enquote{Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?}
The reviewer will then be provided with a series of text boxes and the following prompts:

@@

First, we will derive standardized effect sizes from each individual analysis.
Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
In multi-level models the variance components are partitioned into multiple sources of variation (e.g.~varying intercept of speakers and items, varying by-predictor slopes, etc.).
We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index \(\delta_t\) (where t stands for \enquote{total} variance), which is calculated by the estimated difference between group means (\(\beta\)), divided by the square root of the sum of all variance components as formulated below:

@@

\hypertarget{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}{%
\subsection{Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript}\label{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}}

>>>>

Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.

@@

Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:

@@

First, we will derive standardized effect sizes from each individual analysis.
Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
In multi-level models the variance components are partitioned into multiple sources of variation (e.g.~varying intercept of speakers and items, varying by-predictor slopes, etc.).
We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index \(\delta_t\) (where t stands for \enquote{total} variance), which is calculated by the estimated difference between group means (\(\beta\)), divided by the square root of the sum of all variance components as formulated below:

@@

DESCRIBE META-NALYSIS

We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:

The peer ratings (1-100) of each analysis, a measurement of the \enquote{uniqueness} of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).

The uniqueness of model parameters will be assessed using the Sorensen's Similarity Index (an index typically used to compare species composition across sites). Here we treat model parameters as species and individual analyses as sites. To generate an individual Sorensen's value for each analysis requires calculating the pairwise Sorensen's value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen's values for each analysis. We will calculate the Sorensen's index values using the betapart package (Baselga et al.~2018) in R:

\[\beta_{Sorensen} = \frac{b+c}{2_a + b + c}\]

where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.

The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.

We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).

\hypertarget{step-6-collaborative-write-up-of-manuscript}{%
\subsection{Step 6: Collaborative Write-Up of Manuscript}\label{step-6-collaborative-write-up-of-manuscript}}
